Random forest mill rates

### 2020-04-11 src/modelling - 550/rf_mill.Rmd
changes tax class to factor

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
dat$municipality <- as.factor(dat$municipality)

@@

yhat.bag1 <- predict(rf.as,newdata=test_as)
plot(yhat.bag1, test_as$next.assess, xlab="Predicted Asssessment Value Using Test Set", ylab="Actual Assessment Value")
abline(0,1)
```

>>>>

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
dat$municipality <- as.factor(dat$municipality)
dat$tax.class <- as.factor(dat$tax.class)

@@

yhat.bag1 <- predict(rf.as,newdata=test_as)
plot(yhat.bag1, test_as$next.assess, xlab="Predicted Asssessment Value Using Test Set", ylab="Actual Assessment Value", ylim=c(0, 6e8))
abline(0,1)
```
